Clustering of Last.fm Music

### 2015-05-07 writeup/MSDgroupwriteup.tex
Update MSDgroupwriteup.tex

The MAP@500 scores were computed by calculating the precision between a list of recommendations for a user and that user's test set. Specifically, we calculate the average precision at each element in the list of recommended items (i.e. percentage of correct items among first k recommendations) and sum these up for the first 500 recommendations.
We then averaged the score over all users. Intuitively, the score looks at the percentage of recommendations that were correct (i.e. in the test set) but also takes order into account. So it is preferable to recommend the songs in the user's test set earlier in the list of 500.

We used two different baseline benchmarks to compare our MAP scores against. The first was to simply recommend the top 500 most popular songs to every user. This naive method resulted in a MAP score of 0.0138 (top 500 songs based on number of users who listened to the song) or 0.0126 (top 500 songs based on number of plays the song had). The second method was to first recommend a user the most popular songs of artists the user already had played (but different songs from that artist). If this did not result in enough recommendations, we would then recommend the overall most popular songs as well at the end(similar to baseline method 1). Although this method is conservative in that it does not go beyond the tastes the user has already listened to, it resulted in a significant improvement in the MAP score to 0.045.

>>>>

The MAP@500 scores were computed by calculating the precision between a list of recommendations for a user and that user's test set. Specifically, we calculate the average precision at each element in the list of recommended items (i.e. percentage of correct items among first k recommendations) and sum these up for the first 500 recommendations (i.e. try for each $k \epsilon {1, ..., 500}$).
We then averaged the score over all users. Intuitively, the score looks at the percentage of recommendations that were in-line with the test set of songs actually listened to but also takes order into account. So it is preferable to recommend the songs in the user's test set earlier in the list of 500. Basically, the MAP score is similar to AUC of the ROC curve discussed in class except it takes ordering of the recommendations into account.

We used two different baseline benchmarks to compare our MAP scores against. The first was to simply recommend the top 500 most popular songs to every user. This naive method resulted in a MAP score of 0.0138 (top 500 songs based on number of users who listened to the song) or 0.0126 (top 500 songs based on number of plays the song had). The second method was to first recommend a user the most popular songs of artists the user already had already played (but different songs from that artist). If this did not result in enough recommendations, we would then recommend the overall most popular songs as well at the end (similar to baseline method 1). Although this method is conservative in that it does not go beyond the tastes the user already has in the training set, it resulted in a significant improvement in the MAP score to 0.0448.
